Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-18 papers/B1555_EdgeOn/B1555_letter.tex
reference update and flux ratio description

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems.
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05,V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

@@

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In $K^\prime$ band
imaging (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. The from the edge-on disk can explain why there is no detection of image B \& D in near-infrared (Fig 1, right). Its orientation is aligned with image B \& D. With this new information from AO image, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 2. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 3, Table 3 \& 4.

>>>>

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems.
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05,V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14b}.

@@

To model B1555+375, we use the lens modelling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In $K^\prime$ band
imaging (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. The from the edge-on disk can explain why there is no detection of image B \& D in near-infrared (Fig 1, right). Its orientation is aligned with image B \& D. With this new information from AO image, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. We assume that the lens galaxy has $z_{l}=0.5$ and the source has $z_s=1.5$. The full best-fit parameters are shown in Table 2. Both
of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux ratios. The comparison of observation and our lens modelling is
in Figure 3, Table 3 \& 4.
